\documentclass{article}
    \usepackage[export]{adjustbox}
	\usepackage[english]{babel}%required allways
	\usepackage{booktabs, makecell}	%required for bookstyle tables, without these the tables will have to be redrawn
 \renewcommand\theadfont{\bfseries}
 \renewcommand{\cellalign}{cl}
	\usepackage{bm}
	\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{chngcntr}
	\usepackage{tikz}		% required for linestyle graphics
 %   \usepackage{tikz,pgfplots}	
	\usepackage{enumerate}
	\usepackage{float} 		% required for example and excercise styles
   % \usepackage{chicago}
	\usepackage[round]{natbib}
    \usepackage{epstopdf}
    \usepackage[toc,page]{appendix} % required for adding appendice
	\usepackage[intlimits]{amsmath}%provide option intlimits to
    \usepackage{amsfonts}
							% give boundaries of limits above/below integral sign
	\usepackage{rotating} 	%required for rotated tables
	\usepackage{graphicx} 	%required for including external graphics files
\usepackage{ae,aecompl}
\usepackage{amsmath,amsthm,amssymb,enumerate,mathrsfs}
        \numberwithin{equation}{section}
    \usepackage{epsfig}
\usepackage[pdftex]{hyperref}
	\usepackage{caption}
    \usepackage{multirow}
    \usepackage{epsfig}    %required to put multiple figures under one caption
    \usepackage{lscape}    % change the layout of single page to landscape
    \usepackage{caption}
  %  \usepackage{subcaption}%required to add sub-captions
    \usepackage{subfig}
    \usepackage{setspace}
    \usepackage{url}
    \usepackage{multirow}
    \usepackage{multicol}
    \usepackage{bigstrut}
    \usepackage{natbib}
    \usepackage{bbm}
		\usepackage[a4paper]{geometry}
    \doublespacing
		\geometry{hscale=0.7,vscale=0.75,centering}
\def\R{{\rm I} \negthinspace {\rm R}}
\renewcommand{\baselinestretch}{1.50}\normalsize
\setlength\parindent{0pt}
\theoremstyle{plain}
\newtheorem{ro}{Corollary}
\newtheorem{prop}{Proposition}
\newtheorem{thm}{Theorem}

\theoremstyle{definition}
\newtheorem{de}{Definition}
\newtheorem{lm}{Lemma}
\newtheorem{exm}{Example}
\theoremstyle{remark}
\newtheorem{Alg}{Algorithm}
\newtheorem{rem}{Remark}
\bibliographystyle{agsm}
\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  citecolor=blue,
  urlcolor=blue}
%\doublespace
\let\code=\texttt
\begin{document}

\begin{center}
%\maketitle
\setlength{\unitlength}{2cm}

{\Large Responses to Associate Editor and Referee's Comments \\[%
0pt]
\vspace{0.02in}
\large\textbf{Constructing hierarchical time series through clustering: \\Is there an optimal way for forecasting?}}
\end{center}


\noindent We greatly appreciate the time and effort the Associate Editor and the two referees have dedicated to reviewing our paper. We have provided a reproducibility package in \url{https://github.com/AngelPone/project_hierarchy}.


\newpage


\section*{Comments from Referee 1}

\textit{I am satisfied with the revisions made by the authors in response to my comments. They have addressed all my suggestions thoroughly and clearly, improving the quality of the manuscript.}

\textbf{Response:} Thank you for your review and valuable comments.

\newpage

\section*{Comments from Referee 2}

\textit{Thank you for the clarifications you have provided, I think they are very helpful. The paper is useful and insightful, well done!}

\textbf{Response:} Thank you for your review and valuable comments.

\end{document}